---
title: Line Graph (time series)
author: Judy
date: '2017-09-27'
slug: line-graph-time-series
categories:
  - R
tags:
  - line gragh
  - time serie
  - R Markdown
  - plot
  - Lahman
---
How to use a line graph to display changes over time in selected Lahman baseball database statistics.

First, install packages: Lahman, dplyr, and ggplot2.  Then bring them in with libary: 

First, install packages; dev tools, Lahman, dplyr, ggplot2 and ggiraph.  Then  bring them in with libary: 

```{r}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```
In this example, we extract season homerun totals for Babe Ruth from the Lahman baseball database.  

```{r}
df<-Batting%>%
  filter(playerID=='ruthba01')%>%
  select(yearID,HR)
```
Then we use ggplot to visualize the data.  Years are on the x-axis and homeruns are on the y-axis.  The graph is made interactive for homerun data using tooltip.

```{r}
g<-ggplot()+
  geom_line(data=df,aes(x=yearID,y=HR))+
  geom_point_interactive(data=df,aes(x=yearID,y=HR,tooltip=HR,data_id=yearID))
```
The hover feature with selected color scheme in ggiraph is used to display data at each of the points. 

```{r}
ggiraph(code=print(g),hover_css="fill:white;stroke:red")
```

  
  
