---
title: Dot Plot
author: Judy Minichelli
date: '2017-09-25'
slug: dot-plot
categories:
  - R
tags:
  - R Markdown
  - Lahman
---
How to use an R dot plot to display Lahman database stats.

Comparing number of career homeruns vs. strike outs for all Players.

Dot plot was formated so that hover feature produces first and last name of player at each data point.

First, install packages:  Lahman, dplyr, ggplot2 and ggiraph and bring them in with libary: 

```{r}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

Then build Lahman database queries and view table results for specific categories.  Start with greater than 400 career homeruns vs. strikeouts:

```{r}
df<-Batting%>%
group_by(playerID)%>%
summarize(career_HR=sum(HR),career_SO=sum(SO))%>%

filter(career_HR>=400)
```

Display players first and last name instead of player ID:

```{r}
inner_join(df,Master,by=c("playerID"))%>%
select(nameFirst, nameLast,career_HR,career_SO)
```

Paste the first and last name columns together so the full name is displayed at each "dot" on the plot:

```{r}
HR_vs_SO$name<-paste(HR_vs_SO$nameFirst,HR_vs_SO$nameLast)
```

Now display the dot plot:

```{r}
g<-ggplot()+
geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=name,data_id=nameLast))+
ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")
```

Last, change the color scheme:

```{r}
ggiraph(code=print(g),hover_css="fill:white;stroke:black")
```

