---
title: R Dot Plot
author: Judy Minichelli
date: '2017-09-25'
slug: dot-plot
categories:
  - R
tags:
  - R Markdown
  - Lahman
---
How to use an R dot plot with special features to display selected Lahman baseball database statistics.

In this example, we show number of career homeruns vs. strike outs for all players.  The dot plot is formatted so players first and last names are displayed when the mouse hovers over each dot.

First, install packages; dev tools, Lahman, dplyr, ggplot2 and ggiraph.  Then  bring them in with libary. 

```{r warning=FALSE, message = FALSE}
library(Lahman)
library(dplyr)
library(ggplot2)
library(ggiraph)
```

Then build Lahman database query and view table results for specific categories.  Start with greater than 400 career homeruns vs. strikeouts.

```{r}
df<-Batting%>%
group_by(playerID)%>%
summarize(career_HR=sum(HR),career_SO=sum(SO))%>%

filter(career_HR>=400)
```

Display players first and last name instead of player ID.

```{r}
HR_vs_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,career_HR,career_SO)
```

Paste the first and last name columns together so the full name is displayed at each "dot" on the plot.

```{r}
HR_vs_SO$name<-paste(HR_vs_SO$nameFirst,HR_vs_SO$nameLast)
```

Now display the dot plot using ggplot.

```{r}
g<-ggplot()+
geom_point_interactive(data=HR_vs_SO,aes(x=career_SO,y=career_HR,tooltip=name,data_id=nameLast))+
ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")
```

Last, use ggiraph to activate the hover feature and change the color scheme to increase contrast and make the player names more readable.

```{r}
ggiraph(code=print(g),hover_css="fill:white;stroke:black")
```

